\textsf{Are large language models superhuman chemists?}

### 2024-10-25 src/tex/appendix.tex
Update src/tex/appendix.tex
Co-authored-by: Kevin M Jablonka <32935233+kjappelbaum@users.noreply.github.com>

In addition, as shown in \Cref{tab:cb_skillset} the \chembench corpus can be divided considering the different skills needed to solve the questions. The plot shows an even distribution of the required skills in the \chembench corpus. \Cref{tab:cb_skillset} shows an example question for each skill category.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/CB_SKILL_FIG_V1.pdf}
    \caption{\textbf{Composition of the required skills considered in the \ChemBench corpus.} The circular plot shows the distribution of required skills in the \chembench corpus.}
    \label{fig:cb_skillset}
\end{figure}

>>>>

In addition, as shown in \Cref{tab:cb_skillset} the \chembench corpus can be divided considering the different skills needed to solve the questions. The plot shows a balanced distribution of the required skills in the \chembench corpus. \Cref{tab:cb_skillset} shows an example question for each skill category.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/CB_SKILL_FIG_V1.pdf}
    \caption{\textbf{Composition of the required skills considered in the \chembench corpus.} The circular plot shows the distribution of required skills in the \chembench corpus.}
    \label{fig:cb_skillset}
\end{figure}
